\chapter{Interface}
\section{Interface Milestone 3}
\label{interface3}

\chapter{TeamFound Lizenz}
TeamFound sowie alle enthaltenen Komponenten wie Source-Code, Binaries und Bilder stehen under der GNU General Public License (GPL) Version 2 oder h"oher. Eine Kopie der Lizenz liegt allen Source- und Bin"ar Versionen bei.\\
\\
\textbf{TeamFound - share your search results}\\
\textbf{Copyright \copyright 2005-2006 Jan Kechel, Martin Klink, Jonas Heese, Andreas Bachmann}\\
\\
This program is free software; you can redistribute it and/or
modify it under the terms of the GNU General Public License
as published by the Free Software Foundation; either version 2
of the License, or (at your option) any later version.
This program is distributed in the hope that it will be useful,
but WITHOUT ANY WARRANTY; without even the implied warranty of
MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
GNU General Public License for more details.
You should have received a copy of the GNU General Public License
along with this program; if not, write to the Free Software
Foundation, Inc., 51 Franklin Street, Fifth Floor, Boston, MA 02110-1301, USA.



\begin{thebibliography}{keine ah}
\addcontentsline{toc}{chapter}{Literaturverzeichnis}

\bibitem[Apa02]{} \emph{Apache Ant 1.5.1 Manual}. Apache Software Foundation, http://ant.apache.org/manual/, 2002.
\bibitem[Dat00]{} C. J. Date. \emph{An Introduction to Database Systems}. Addison Wesley, 2000.
\bibitem[ExFF]{} \emph{Extend Firefox}. Mozilla, http://developer.mozilla.org/mozilla-org/contests/extendfirefox/documentation.php
\bibitem[FFTT]{} \emph{Firefox Toolbar Tutorial}. Born Geek, http://www.borngeek.com/firefox/toolbar-tutorial/
\bibitem[Fri97]{} Jeffrey E. F. Friedl. \emph{Mastering Regular Expressions}. O'Reilly, 1997.
\bibitem[Gswed]{} \emph{Getting started with extension development}. mozillaZine, http://kb.mozillazine.org/Getting\_started\_with\_extension\_development.
\bibitem[Goo00]{} M. Goossens, F. Mittelbach und A. Samarin. \emph{Der \LaTeX \ Begleiter}. Addison Wesley, 2000.
\bibitem[LucQS]{} \emph{Apache Lucene Query Syntax}. Apache Software Foundation http://lucene.apache.org/java/docs/queryparsersyntax.html .
\bibitem[Oua02]{} S. Oualline. \emph{Vi IMproved -- Vim}. New Riders, 2002 .
\bibitem[PolPos]{} \emph{PolePosition}. the open source database benchmark http://www.polepos.org.
\bibitem[Roac04]{} Eric. \emph{How to create Firefox extensions}. roachfiend.com, http://roachfiend.com/archives/2004/12/08/how-to-create-firefox-extensions
\bibitem[Spo01]{} J. Spolsky. \emph{User Interface Desing for Programmers}. Apress, 2001 .
\bibitem[XULPL]{} \emph{XUL Planet} XUL Planet, http://xulplanet.com .

\end{thebibliography}

